%&<latex>
\documentclass[letterpaper,12pt]{article}

\pdfpagewidth = 8.5in
\pdfpageheight = 11.0in
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{setspace}
\usepackage{xspace}
\usepackage{authblk}

\pagestyle{plain}
\pagenumbering{arabic}

\usepackage[round]{natbib}
\usepackage{hyperref}
% \hypersetup{pdfborder={0 0 0}, colorlinks=true, urlcolor=black, linkcolor=black, citecolor=black}
\hypersetup{pdfborder={0 0 0}, colorlinks=true, urlcolor=blue, linkcolor=blue, citecolor=blue}

\newcommand{\highLight}[1]{\textcolor{magenta}{\MakeUppercase{#1}}}
\newcommand{\ignore}[1]{}
\newcommand{\super}[1]{\ensuremath{^{\textrm{#1}}}}
\newcommand{\sub}[1]{\ensuremath{_{\textrm{#1}}}}
\newcommand{\dC}{\ensuremath{^\circ{\textrm{C}}}}
\newcommand{\croc}{\emph{Crocodile}\xspace}

\title{Book review---Crocodile}

\author[1]{Jamie R.\ Oaks\thanks{Corresponding author: \href{mailto:joaks1@gmail.com}{\tt joaks1@gmail.com}}}

\affil[1]{Department of Biology, University of Washington, Seattle, Washington 98195}

\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

\newpage
\doublespacing

\croc by Dan Wylie \citep{Wylie2013} is part of the ``Animal'' series of books
published by Reaktion Books and edited by Jonathon Burt.
\croc is my initiation to this series, and I am hooked.
The author uses the extant species of crocodylians found around the globe as a
conduit into human history, culture, and psychology.

In the first chapter, Dr.\ Wylie provides an overview
of the diversity, evolution, and biology of crocodylians and their ancestors.
He creatively surveys the basic biology of the crocodile in the order of the
anatomical structures of the animal you would encounter if unlucky enough to
become its prey.
Throughout the first chapter, Dr.\ Wylie interleaves human perception of
crocodiles, foreshadowing subsequent chapters that explore in detail the
cultural role of crocodiles throughout human history.

The subsequent chapters are organized by geography, visiting each continent,
starting in Africa and working westward.
At the beginning of each chapter, Dr.\ Wylie provides a brief overview of the
natural history and conservation status of each species within the region.
He then delves into the long history of crocodiles in the culture, religion and
psychology of the people of the region.

There are some minor errors regarding taxonomy and natural history, however,
the author has clearly done his homework.
In general, the biology of crocodiles takes a back seat to the real emphasis of
this book: the interplay of crocodiles and humans over time and space.
The author's research into this subject is impressive, referencing works as
diverse as ancient Egyptian papyrus to youTube.

Dr.\ Wylie takes advantage of the unique perspective that crocodiles provide
to our own species.
Crocodylians represent the most widely distributed group of terrestrial animals
that occasionally predate on humans.
Not surprisingly, this has made crocodiles ubiquitous in human culture
throughout history.
From reverence and fear to hatred and exploitation, crocodiles have filled
nearly every niche in the human psyche, from gods to foes to fashion
accessories.

\bibliographystyle{evolution}
\bibliography{references}

\end{document}

